\sys: Automated Data-Parallel Shell Processing

### 2020-04-07 pldi/draft.tex
Placeholder for the unix50 subsection

\TODO{Notes on Unix50. We got the Unix50 solutions as is and we ran
  them. These are the numbers. By changing fmt -w1 to tr (or by adding
  it appropriately to the DSL) and by changing some occurences of awk
  to ..., the speedup in these cases goes to...}

@@

@@

In terms of execution time, with two Hadoop datanodes running on Hadoop 3.2.1 and Openjdk 11.0.5 without any replication (\ie fault-tolerance), the Hadoop program takes 6m22s for data processing and 1m09s for moving the dataset to HDFS.
For the same amount of parallelism, \sys takes 4m30.554s---but this includes downloading and uncompressing the data files.

>>>>

@@

\subsection{Unix50}
\label{unix50}

The goal of this subsection is to evaluate \sys on an existing set of
unix pipelines found in the wild. \todo{Motivate why unix50 is a nice
  set of pipelines.} We took the solutions for the unix50 from
\todo{Ref} and we executed them \emph{without any modification} with
\sys's parallelism set to \todo{X}. The input given to the pipelines
was the test input from unix50 multiplied \todo{10000} times. The
speedup of each pipeline separately is shown in \todo{ref}. The
average\todo{/median} speedup is \todo{X}.

All pipelines that perform poorly (\todo{enumerate them}) contain
non-parallelizable commands. An illustrative example is pipeline
\todo{X}, which is shown here:

\begin{lstlisting}[language=sh, float=h, numbers=none]
  TODO
\end{lstlisting}

Notice in the above the use of (awk, fmt, or something else). We
noticed that these occured in other pipelines too. By changing them to
\todo{X}, the average speedup of these pipelines improved to \todo{x}
and the new total average speedup is \todo{X}.

\subsection{Comparison}

\todo{Include comparison with Niko's speeduptest, with gnu-parallel,
  with sort -parallel (and possibly other commands that have parallel
  flags), and finally with Raftlib.}

@@

In terms of execution time, with two Hadoop datanodes running on Hadoop 3.2.1 and Openjdk 11.0.5 without any replication (\ie fault-tolerance), the Hadoop program takes 6m22s for data processing and 1m09s for moving the dataset to HDFS.
For the same amount of parallelism, \sys takes 4m30.554s---but this includes downloading and uncompressing the data files. \kk{I think it is fine keeping the Hadoop evaluation here, since this macrobenchmark was taken from a Hadoop book.}
